---
title: "Excercise_1"
author: "Aleksandra Lubicka"
date: "14/04/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# TITLE
```{r logo, echo=FALSE, out.width = '80%'}
knitr::include_graphics("/Users/alubis/Desktop/OneDrive/DS sem II/rep_res/Friends_logo.svg")
```

*Friends* is an American television sitcom, created by David Crane and Marta Kauffman, which aired on NBC from September 22, 1994, to May 6, 2004, lasting ten seasons. With an ensemble cast starring Jennifer Aniston, Courteney Cox, Lisa Kudrow, Matt LeBlanc, Matthew Perry and David Schwimmer, the show revolves around six friends in their 20s and 30s who live in Manhattan, New York City. The series was produced by Bright/Kauffman/Crane Productions, in association with Warner Bros. Television. The original executive producers were Kevin S. Bright, Kauffman, and Crane.

# RATINGS
The table below shows the ratings of Friends in the United States, where it consistently ranked within the top ten of the final television season ratings.[104] "Rank" refers to how well Friends rated compared to other television series that aired during primetime hours of the corresponding television season. It is shown in relation to the total number of series airing on the then-six major English-language networks in a given season. "Viewers" refers to the average number of viewers for all original episodes, broadcast during the television season in the series's regular timeslot. The "season premiere" is the date that the first episode of the season aired, and the "season finale" is the date that the final episode of the season aired. So far, Friends has been the last sitcom to reach the no. 1 spot on television, as its successors were CSI: Crime Scene Investigation, American Idol, NBC Sunday Night Football, and NCIS. Following the September 11 attacks, ratings increased 17% over the previous season.

| Season    | Timeslot    | Year    | Viewers |
|:----------|:------------|:--------|:--------|
| 1	        | September 22| 1994    | 31,3    |
| 2	        | September 21| 1995    | 52,9    |
| 3	        | September 19| 1996    | 29,8    |
| 4	        | September 25| 1997    | 31,6    |
| 5	        | September 24| 1998    | 30,9    |
| 6	        | September 23| 1999    | 30,7    |
| 7	        | October 12  | 2000    | 30,1    |
| 8	        | September 27| 2001    | 34,9    |
| 9	        | September 26| 2002    | 34      |
| 10        | September 25| 2003    | 52,5    |

## GRAPH OF THE VIEWERSHIP
```{r}
dat <- read.table(text=
"Season Timeslot Year Viewers
1 September 1994 31.3
2 September 1995 52.9
3 September 1996 29.8
4 September 1997 31.6
5 September 1998 30.9
6 September 1999 30.7
7 October 2000 30.1
8 September 2001 34.9
9 September 2002 34
10 September 2003 52.5", header = T, stringsAsFactors = FALSE)

plot(dat$Year, dat$Viewers)
```


## GRAPH SEASON-TO-SEASON

```{r}
plot(dat$Season, dat$Viewers)

roznica= max(dat$Viewers) - min(dat$Viewers)
```
The biggest difference in viewership between the seasons was `r roznica` mln.

